Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
paper beautification

\begin{abstract}
%
We present a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals by the controller.  The approach works in two
stages, leveraging counterexample guided inductive synthesis (CEGIS) and
reachability analysis.  CEGIS synthesizes a static feedback controller that
stabilizes the system under some restrictions given by the safety of the
reach space.  Safety is verified either via BMC or abstract acceleration; if
the verification step fails, we generate an alternative controller by
generalizing the counterexample.  We synthesize stable and safe controllers
for intricate physical plant models from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesize safe 
digital state-feedback controls
and prove their soundness by encompassing errors due to digitalization and quantization effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

%% we substitute the second step by employing abstract
%% acceleration to unfold the dynamics forward, instead of symbolically
%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
%\todo{We need to emphasize the derivation of errors for soundness. Can we claim completeness already?}

@@

%To this end, we formalize the notion of solution generalization for
%Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
%of abstraction refinement in order to achieve scalability.
%This strategy enables the inductive generalization engine inside CEGIS
%to look for candidate solutions in a reduced solution space.

@@

The tool Pessoa~\cite{mazo2010pessoa} synthesizes
correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the abstraction
of a physical system to an equivalent finite-state machine and on the
computation of reachability properties over the finite-state machine.  Based
on this safety specification over state values, Pessoa can synthesize
embedded controller software for a range of properties.
The embedded controller software can be more complicated than
the state feedback control we synthesized, and the properties 
available cover more detail.
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the quantization error
introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
synthesizing fixed-point digital controllers.

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback control algorithm, 
as implemented on modern Field-Programmable Gate Arrays or Digital Signal Processors. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a state feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop discrete dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behavior \cite{astrom1997computer}. 
As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.

@@

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS.  For this purpose, we first
provide the synthesizer's general architecture, followed by describing
our two approaches to synthesizing safe controllers:
the first one is a baseline approach which relies on a naive explicit
unwinding of the transition relation, whereas the second uses an
abstraction to implicitly evaluate all possible progressions of the
system simultaneously. % on an infinite time horizon.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
$\exists P .  \forall x.  \sigma(x, P)$, 
where $P$ ranges over functions, 
$x$ ranges over ground terms, 
and $\sigma$ is a quantifier-free formula.  
We interpret the ground terms over some finite domain $\mathcal{D}$.
%
The design of our synthesizer consists of two phases, an inductive
synthesis phase and a validation phase, which interact via a finite
set of test vectors {\sc inputs} that is updated incrementally.  Given
the aforementioned specification $\sigma$, the inductive synthesis
procedure tries to find an existential witness $P$ satisfying
the specification $\sigma(x, P)$ for all $x$ in {\sc
  inputs} (as opposed to all $x \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to the validation phase, which checks
whether it is a full solution (i.e., $P$ satisfies the
specification $\sigma(x, P)$ for all
$x\in\mathcal{D}$).  If this is the case, then the algorithm
terminates.  Otherwise, additional information is provided to the
inductive synthesis phase in the form of a new counterexample that is
added to the {\sc inputs} set and the loop iterates again.
More details about the general architecture of the synthesizer can
be found in~\cite{DBLP:conf/lpar/DavidKL15}.
%% It is worth noting that each iteration of the loop adds a new input to
%% the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
%% that the full set of inputs $\mathcal{D}$ is finite, this means that
%% the refinement loop can only iterate a finite number of times.

@@

\item The first {\sc verify} stage, {\sc safety}, checks that candidate
solution $K$, which we synthesized to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
state within $k$ steps where we assume $k$ to be under the completeness threshold. 
After unwinding the transition system corresponding to the previously synthesized controller
$k$ steps, we check that the safety specification holds for any initial state.

@@

  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
  %uses a multi-staged verification phase and performs solution generalization based on
%the plant precision, the number of loop unrollings, 
  %and the sampling rate. Essentially, it
  synthesizes a controller for an individual initial state
and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
inputs, and time horizons during the verification phase.
Essentially, this approach relies on the explicit
simulation over a bounded time horizon of individual states that form
part of an uncountable space and tries to generalize it for an
infinite space over an infinite time horizon.

@@

\end{enumerate}
\item In the {\sc synthesize} phase, we synthesize a candidate controller
%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
% specification defined by Jury's 
%criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.
  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
  $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
%%   We obtain it by solving the SAT formula 
%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
%% that satisfies the input constraint and Jury's criteria for 
%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
If there is no candidate solution we return UNSAT and exit the loop.
\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
  %
  of the 
  %consisting of evaluating the
  progression of the system from $\phi_{init}$ over time,
$x_{k+1} \models \phi_{safety}$. %% For this purpose we require 
%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
%% from which the system progresses.
% Obviously, this set $x_0$ 
% must satisfy the specification; otherwise, the system will be unsafe to begin with.
% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
% The presence of $\mat{T}$ is because this will typically be given in the original 
% state-space.
%% Next, we use abstract acceleration to get a second abstraction that 
  %% encompasses the accelerated continuous reach-tube over an unbounded time.
  In order to compute the progression of point $x_0$ at iteration $k$,
  we accelerate the dynamics of the closed-loop system and obtain:
  %we take the
  %the closed-loop model:
  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
  %and accelerate it to:
%
\begin{align}
%\label{eq:acc_observer_LTI_cf}
x=&(A_d-B_dK)^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1\ 1 \cdots \ 1 ]^T
\end{align}
As this still requires us to verify the system for every $k$ up to infinity, 
we use abstract acceleration again to obtain
the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_{init}$:
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
\end{align}
%
where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system \cite{cattaruzza2015unbounded}, whereas the set N is non-deterministically chosen.

@@

\subsubsection{Illustrative Example}
%
Let us take the Helicopter example in Table \ref{table:State-space benchmarks} with discretized dynamics
$$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
Using the initial state bounds $\underline{x_{0}}=-0.9$ and $\overline{x_{0}}=0.9$, the input bounds $\underline{u}=-10$ and $\overline{u}=10$, and safety specifications 
$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesizes an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification
$(k,x_0) \in \{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]), (3, [\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$.
This allows the {\sc abstract} phase to create a new safety specification that considers these iterations for these initial states to constrain the solution space.
This refinement allows {\sc synthesize} to find a controller $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$, which this time passes the verification phase, resulting in a safe system.

>>>>

\begin{abstract}
%
We present a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals by the controller.  The approach works in two
stages, leveraging counterexample guided inductive synthesis (CEGIS) and
reachability analysis.  CEGIS synthesises a static feedback controller that
stabilizes the system under some restrictions given by the safety of the
reach space.  Safety is verified either via BMC or abstract acceleration; if
the verification step fails, we generate an alternative controller by
generalizing the counterexample.  We synthesize stable and safe controllers
for intricate physical plant models from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesise safe 
digital state-feedback controls
and prove their soundness by encompassing errors due to digitalization and quantization effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

%% we substitute the second step by employing abstract
%% acceleration to unfold the dynamics forward, instead of symbolically
%% unwinding the transition relation~\cite{cattaruzza2015unbounded}.
%\todo{We need to emphasise the derivation of errors for soundness. Can we claim completeness already?}

@@

%To this end, we formalise the notion of solution generalization for
%Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
%of abstraction refinement in order to achieve scalability.
%This strategy enables the inductive generalization engine inside CEGIS
%to look for candidate solutions in a reduced solution space.

@@

The tool Pessoa~\cite{mazo2010pessoa} synthesizes
correct-by-design embedded control software, in a Matlab ToolBox.  It is based on the abstraction
of a physical system to an equivalent finite-state machine and on the
computation of reachability properties over the finite-state machine.  Based
on this safety specification over state values, Pessoa can synthesize
embedded controller software for a range of properties.
The embedded controller software can be more complicated than
the state feedback control we synthesised, and the properties 
available cover more detail.
%based on a safety specification over state values, as well as specification on characteristic functions of the controller. 
However, Pessoa does not have native inclusion of the quantization error
introduced by Digital-to-Analogue/Analogue-to-Digital conversion needed for
synthesizing fixed-point digital controllers.

@@

Models \eqref{eq:ode} and \eqref{eq:plant} depend on external non-determinism in the form of input signals $u (t), u_k$, respectively. 
Feedback architectures can be employed to manipulate the properties and behaviors of the continuous process (the plant).   
%reduce the effect of parametric uncertainties and attenuate the effects of noise and disturbance. 
We are interested in the synthesis of digital feedback control algorithm, 
as implemented on modern FPGAs or Digital Signal Processorss. 
The most basic feedback architecture is the state feedback, 
where the control action $u_k$ (notice we work with the discretized signal) is computed by: 
%
\begin{equation}
\label{eq:controlaction}
u_k = r_{k} - K x_k. 
\end{equation}
%
Here $K \in \mathbb{R}^{m \times n}$ is a state feedback gain matrix, 
and $r_{k}$ is a reference signal (again digital).   
%
The closed-loop model then takes the form 
\begin{align}
\label{eq:closedloopss}
x_{k+1} = ( A_d - B_d K ) x_k + B_d r_k.
\end{align}
The gain matrix $K$ can be set so that the closed-loop discrete dynamics are shaped as desired, 
for instance according to a specific stability goal or around a specific dynamical behavior \cite{astrom1997computer}. 
As argued later in this work, we will target more complex objectives, such as quantitative safety requirements that are not typical in the digital control literature. 
Further, we will encompass the digital nature of the controller, which manipulates quantities with finite precision.

@@

In this section, we describe our technique for synthesizing safe
digital feedback controllers using CEGIS.  For this purpose, we first
provide the synthesiser's general architecture, followed by describing
our two approaches to synthesizing safe controllers:
the first one is a baseline approach which relies on a naive explicit
unwinding of the transition relation, whereas the second uses an
abstraction to implicitly evaluate all possible progressions of the
system simultaneously. % on an infinite time horizon.

@@

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\subsection{General architecture of the program synthesizer}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\label{synthesizer-general}
The input specification provided to the program synthesizer is of the form
%$\exists P .  \forall \vec{x}.  \sigma(\vec{x}, \vec{P})$ 
$\exists P .  \forall x.  \sigma(x, P)$, 
where $P$ ranges over functions, 
$x$ ranges over ground terms, 
and $\sigma$ is a quantifier-free formula.  
We interpret the ground terms over some finite domain $\mathcal{D}$.
%
The design of our synthesizer consists of two phases, an inductive
synthesis phase and a validation phase, which interact via a finite
set of test vectors {\sc inputs} that is updated incrementally.  Given
the aforementioned specification $\sigma$, the inductive synthesis
procedure tries to find an existential witness $P$ satisfying
the specification $\sigma(x, P)$ for all $x$ in {\sc
  inputs} (as opposed to all $x \in \mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this
witness is a candidate solution to the full synthesis formula.  We
pass this candidate solution to the validation phase, which checks
whether it is a full solution (i.e., $P$ satisfies the
specification $\sigma(x, P)$ for all
$x\in\mathcal{D}$).  If this is the case, then the algorithm
terminates.  Otherwise, additional information is provided to the
inductive synthesis phase in the form of a new counterexample that is
added to the {\sc inputs} set and the loop iterates again.
More details about the general architecture of the synthesiser can
be found in~\cite{DBLP:conf/lpar/DavidKL15}.
%% It is worth noting that each iteration of the loop adds a new input to
%% the finite set $\text{\sc inputs}$ that is used for synthesis.  Given
%% that the full set of inputs $\mathcal{D}$ is finite, this means that
%% the refinement loop can only iterate a finite number of times.

@@

\item The first {\sc verify} stage, {\sc safety}, checks that candidate
solution $K$, which we synthesised to be safe for at least one initial state, is safe for \emph{all} possible initial states, i.e., does not reach an unsafe
state within $k$ steps where we assume $k$ to be under the completeness threshold. 
After unwinding the transition system corresponding to the previously synthesized controller
$k$ steps, we check that the safety specification holds for any initial state.

@@

  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
  %uses a multi-staged verification phase and performs solution generalization based on
%the plant precision, the number of loop unrollings, 
  %and the sampling rate. Essentially, it
  synthesises a controller for an individual initial state
and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
inputs, and time horizons during the verification phase.
Essentially, this approach relies on the explicit
simulation over a bounded time horizon of individual states that form
part of an uncountable space and tries to generalize it for an
infinite space over an infinite time horizon.

@@

\end{enumerate}
\item In the {\sc synthesize} phase, we synthesise a candidate controller
%We begin with a minimum set of linear inequalities describing the constraints caused by the input and the initial state during a single iteration, in addition to a stability 
% specification defined by Jury's 
%criteria. %, and try to synthesise a controller that meets these specs.
% For a stabilized closed-loop, which is necessary for our safety property, we need
% these roots to remain within the unit circle, which we verify using Jury's criteria.
% Notice that in our polynomials $c_0=1$ and we only use reals.
% Once we have established convergence, we may examine the 
% safety specification $\phi_{safety}$.
  $K \in \mathbb{R}\langle I_c,F_c\rangle^n$ that satisfies
  $\phi_{stability} \wedge \phi_{safety} \wedge \phi_{init}^{K}$ by invoking a SAT solver.
%%   We obtain it by solving the SAT formula 
%% $$\mathcal{J}_K=\mathcal{J}\langle I,F \rangle (P_{a-k},\mat{T})\wedge \phi_{safety}$$ 
%% that satisfies the input constraint and Jury's criteria for 
%% $P_{a-k}=z^n+\sum_{i=1}^n (a_i-k_i) z^{n-i} : k_i \in \mat{K} \wedge \tilde{\mat{K}}=\mat{K}\mat{T}$,
%% where $\mathcal{J}\langle I,F \rangle (P,\mat{T})$ is a program describing Jury's method.
If there is no candidate solution we return UNSAT and exit the loop.
\item Once we have a candidate solution, we perform a safety verification % If this step fails, we find a counterexample iteration and initial state and create a new constraint to refine our abstraction.
  %
  of the 
  %consisting of evaluating the
  progression of the system from $\phi_{init}$ over time,
$x_{k+1} \models \phi_{safety}$. %% For this purpose we require 
%% an initial set $\phi_{init}= x_0 \in [\underline{x_0} \ \overline{x_0}]$ 
%% from which the system progresses.
% Obviously, this set $x_0$ 
% must satisfy the specification; otherwise, the system will be unsafe to begin with.
% We accept a specification in the form $\mat{E}\mat{T}x_0<\mat{f}$. 
% The presence of $\mat{T}$ is because this will typically be given in the original 
% state-space.
%% Next, we use abstract acceleration to get a second abstraction that 
  %% encompasses the accelerated continuous reach-tube over an unbounded time.
  In order to compute the progression of point $x_0$ at iteration $k$,
  we accelerate the dynamics of the closed-loop system and obtain:
  %we take the
  %the closed-loop model:
  %$x_{k+1}=\mat{A}_{t}x_k+\mat{B}_{n} (\nu_1 + \nu_2 + \nu_3)$
  %and accelerate it to:
%
\begin{align}
%\label{eq:acc_observer_LTI_cf}
x=&(A_d-B_dK)^kx_0
%+\sum_{i=0}^{k-1} \mat{A}_t^i \mat{B}_{t} r_i
+\sum_{i=0}^{k-1} (A_d-B_dK)^i B_{n}(\nu_1+\nu_2+\nu_3) : B_n= [1\ 1 \cdots \ 1 ]^T
\end{align}
As this still requires us to verify the system for every $k$ up to infinity, 
we use abstract acceleration again to obtain
the reach-tube, i.e., the set of all reachable states at all times given an initial set $\phi_{init}$:
\begin{align}
\label{eq:aa_observer_LTI_cf}
\hat{X}^\#
=&\mathcal{A} X_0 + \mathcal{B}_{n} N\\
X_0 =&\left \{x : x \models \phi_{init} \right\}\nonumber
\end{align}
%
where $\mathcal{A}=\bigcup_{k=1}^\infty (A_d-B_dK)t^k, \mathcal{B}_{n}=\bigcup_{k=1}^\infty \sum_{i=0}^k(A_d-B_dK)^iB_{n}$ are abstract matrices for the closed-loop system \cite{cattaruzza2015unbounded}, whereas the set N is non-deterministically chosen.

@@

\subsubsection{Illustrative Example}
%
Let us take the Helicopter example in Table \ref{table:State-space benchmarks} with discretized dynamics
$$A_d = \left[\begin{array}{ccc}2.6207&-1.1793&0.65705\\2&0&0\\0&0.5&0\end{array}\right], B_d = \left [\begin{array}{c}8\\0\\0\end{array}\right]$$
Using the initial state bounds $\underline{x_{0}}=-0.9$ and $\overline{x_{0}}=0.9$, the input bounds $\underline{u}=-10$ and $\overline{u}=10$, and safety specifications 
$\underline{x_{i}}=-0.92$ and $\overline{x_{i}}=0.92$, the {\sc synthesize} phase in Fig.~\ref{fig:CEGARIS} synthesises an initial candidate controller $K=[\begin{array}{ccc}0.24609375&-0.125&0.1484375\end{array}]$.
Although this candidate is stable, the {\sc verify} phase finds it to be unsafe and returns a list of iterations with an example initial state that fails the safety specification
$(k,x_0) \in \{ (2, [\begin{array}{ccc}0.9&-0.9&0.9\end{array}]), (3, [\begin{array}{ccc}0.9&-0.9&-0.9\end{array}])\}$.
This allows the {\sc abstract} phase to create a new safety specification that considers these iterations for these initial states to constrain the solution space.
This refinement allows {\sc synthesize} to find a controller $K=[\begin{array}{ccc}0.23828125&-0.17578125&0.109375\end{array}]$, which this time passes the verification phase, resulting in a safe system.
